Glyph-maps for visualizing climate data and models

### 2011-09-22 paper.tex
perception section

\begin{figure*}[htp]
\centerline{\includegraphics[width=6in]{nasa-colored-map.png}}
\caption{Facetted map of de-seasonalized temperature.}
\label{fig:facetted-map}
\end{figure*}

@@

*** Re-visit this next paragraph - its a little too airy-fairy, and the plot with color needs to have the color dampened more. Its way too dominant.

It's also often useful to display other types of reference information. You are only limited by your imagination (and the capabilities of your graphics software), but two simple ideas are to (1) vary the colour or transparency of glyphs or references, or (2) use an additional layer to highlight special points. Figure~\ref{fig:ref-adv} illustrates these ideas to display the month with the highest temperature at each locations. Careful colour choice is necessary so that this information is perceptible, but not distracting.

\begin{figure}[htbp]
  \centering
  \includegraphics[width=0.5\linewidth]{ref-max-1}%
  \includegraphics[width=0.5\linewidth]{ref-max-2}
  \caption{Glyph-maps of seasonal temperature patterns also showing the month with the highest temperature using (left) an additional layer of points and (right) changing the background colour of the reference grid.}
  \label{fig:ref-adv}
\end{figure}

A particularly useful summary when to add when displaying model predictions, is some measure of model fit. This makes it easier to avoid over-interpreting predictions from poorly-fitting models.

*** Adding a circular reference line helps to pick out these deviations.

@@

Compare the facetted map Fig 1 with the glyph-map of de-seasonalized data

@@

>>>>

\begin{figure*}[htp]
\centerline{\includegraphics[width=6in]{nasa-colored-map.png}}
\caption{Facetted map of de-seasonalized temperature. The dominant feature is the El Ni\~no warming in the qouthern equatorial region in the last half of 1997 and first half of 1998. Smaller features are only noticeable on closer inspection, or if pointed out: such as the relative warming on the mountain regions in south and north America in the later years.}
\label{fig:facetted-map}
\end{figure*}

@@

%*** Re-visit this next paragraph - its a little too airy-fairy, and the plot with color needs to have the color dampened more. Its way too dominant. This paragraph is too speculative for the paper, so removing it from first draft.

%It's also often useful to display other types of reference information. You are only limited by your imagination (and the capabilities of your graphics software), but two simple ideas are to (1) vary the colour or transparency of glyphs or references, or (2) use an additional layer to highlight special points. Figure~\ref{fig:ref-adv} illustrates these ideas to display the month with the highest temperature at each locations. Careful colour choice is necessary so that this information is perceptible, but not distracting.

%\begin{figure}[htbp]
%  \centering
%  \includegraphics[width=0.5\linewidth]{ref-max-1}%
%  \includegraphics[width=0.5\linewidth]{ref-max-2}
%  \caption{Glyph-maps of seasonal temperature patterns also showing the month with the highest temperature using (left) an additional layer of points and (right) changing the background colour of the reference grid.}
%  \label{fig:ref-adv}
%\end{figure}

%A particularly useful summary when to add when displaying model predictions, is some measure of model fit. This makes it easier to avoid over-interpreting predictions from poorly-fitting models.

%*** Adding a circular reference line helps to pick out these deviations.

@@

Compare the facetted map Figure \ref{facetted-map} with the glyph-map
of de-seasonalized data in Figure \ref{fig:nasa-deseas-glyph}.

@@

\begin{figure*}[htp]
\centerline{\includegraphics[width=6in]{nasa-deseas-glyph.png}}
\caption{Glyph-map of de-seasonalized temperature, to compare with Figure \ref{facetted-map}. }
\label{fig:nasa-deseas-glyph}
\end{figure*}
